Example of Market Simulator Dasbhaord

### 2021-09-22 README.Rmd
Long-awaited README update

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

Title <- "Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy"
Authors <- "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
Year <- "2019"
```

@@

[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Christopher Newport University  
[Marc Dotson](https://marriottschool.byu.edu/directory/details?id=50683) • Brigham Young University  
[Andrew Heiss](https://www.andrewheiss.com) • Brigham Young University

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 3
)

Title <- "Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy"
Authors <- "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
Year <- "2021"
```

@@

[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Lewis & Clark College  
[Marc Dotson](https://marriottschool.byu.edu/directory/details?id=50683) • Brigham Young University  
[Andrew Heiss](https://www.andrewheiss.com) • Georgia State University

@@

**NB: These instructions are all out of date and will be updated to match how the project is actually run, eventually. We're converting this project from a `make`-based build system to a [{targets}](https://books.ropensci.org/targets/)-based build system, which is easier to manage and requires fewer external dependencies.**

*This stuff is accurate*:

Because the posterior draws from the models are large and take forever to make, we've saved the results as `.rds` files. However, because those files are fairly big and we don't want to track them with git, we've stored them at this project's [OSF page](https://osf.io/r59xz/) in [OSF's internal storage system](https://osf.io/r59xz/files/). Running `targets::tar_make(starts_with("file_"))` (or just `targets::tar_make()` in general) will trigger a function (`get_from_osf()`) that will automatically download all the `.rds` files and place them in `data/raw_data/posterior_draws`, which is not tracked by git (and which should be set to not sync in Dropbox).

*This stuff is out of date*:
